Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-05-10 Master Thesis/synopsis.tex
Add abstracts

\begin{proof}
(i) and (ii) follow from [HK], Lemma 2.4.3 and (iii) is a consequence of (ii) and [EGA IV] 18.6.14.
\end{proof}

>>>>

\begin{proof}
(i) and (ii) follow from [HK], Lemma 2.4.3 and (iii) is a consequence of (ii) and the fact that henselizations commute with filtrated direct limits, see \cite{EGA4} 18.6.14.
\end{proof}

### 2017-05-10 Master Thesis/thesis.tex
Add abstracts

\vspace*{0cm}
\vfill
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur interdum, dui non molestie tincidunt, lectus enim aliquet arcu, suscipit pulvinar dui tortor vitae mi. Nam cursus mi sem, ac gravida tellus congue vitae. Nam elementum eleifend lorem dignissim rhoncus. Quisque ac nulla dui. Duis rutrum eros ornare faucibus congue.
\end{abstract}

@@

\renewcommand{\abstractname}{Zusammenfassung}
\begin{abstract}
Integer congue euismod justo, quis venenatis tortor. Proin sem leo, accumsan eget pulvinar vitae, tincidunt ut elit. Morbi ut purus volutpat, efficitur quam id, consequat augue. Cras ullamcorper lacus eget massa vehicula, a elementum diam lacinia. Morbi efficitur elementum malesuada. Cras a aliquam tortor, et interdum neque.
\end{abstract}
\vfill
\clearpage

>>>>

\vspace*{0cm}
\vfill
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
In this thesis we will follow M. Spiess' argument and present his purely arithmetic proof of the fact that isomorphisms between the absolute Galois groups of function fields of transcendence degree $1$ over number fields are induced by field isomorphisms between these fields.
\end{abstract}

@@

\renewcommand{\abstractname}{Zusammenfassung}
\begin{abstract}
In dieser Arbeit wollen wir M. Spiess' rein arithmetischer Beweis nachgehen und zeigen, wieso Isomorphismen zwischen den absoluten Galoisgruppen von Funktionenkörpern vom Transzendenzgrad $1$ über Zahlkörper schon von Körperisomorphismen zwischen diesen Körpern induziert werden.
\end{abstract}
\vfill
\clearpage
